---
title: "NIS-intro-detect-report-sensitivity"
output: html_document
params:
  user_inputs: config
  sensitivity_inputs: sens
  factors: factors
  df_factors_all: df_factors_all
  defaults: defaults
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("ggplot2")
library("patchwork")
```
\

**Date:** `r Sys.time()` \
**Author:** `r params$user_inputs$user` \
**Run Name:** `r params$user_inputs$run_name` \

\

The sensitivity of each parameter within the NIS-intro-detect-sim script is tested and reported.

Three scenarios for site surveillance to detect non indigenous species (NIS) introduction are presented and the time to detection is reported.

* **A.** Random surveillance, where sites are visited at an equal rate independent of the risk of NIS introduction and establishment at each site.

* **B.** Risk-based surveillance, where sites with a higher probability of NIS introduction and establishment are visited at a higher visit rate due to their elevated risk.

* **C.** Heavy risk-based surveillance, where sites with higher probability of NIS introduction and establishment form the main focus of surveillance programmes and are visited at a 


\

#### Input Parameters

```{r, echo = FALSE}
setNames(stack(params$user_inputs)[2:1], c("Parameter Name", "Input Value"))
```

\

#### Default Sensitivity Parameters

The default parameters used for each run were as follows:

```{r, echo = F}
params$defaults
```

\

#### Input Sensitivity Parameters

The ranges and intervals used to produce different values for each of the parameters used in the sensitivity test.

```{r, echo = FALSE}
data_frame <- as.data.frame(do.call(rbind, params$sensitivity_inputs))
data_frame
```

\

#### Sensivity Analysis

```{r sensivitiy, echo = FALSE, fig.width = 12, fig.height = 4, fig.align = 'center', warnings = FALSE}
# produce plots for each sensitivity factor tested
plots <- lapply(names(params$df_factors_all), function(w) {
  
  df_factors <- params$df_factors_all[[w]]
  
  lapply(params$factors, function(x) {
    
  # violin plot - time taken to detect NIS where detection != 100
  p1 <- ggplot2::ggplot(df_factors[[x]],
                        aes(x = name, y = value, fill = name)) +
    geom_violin() +
    theme_bw() +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
    scale_x_discrete(name = params$factors[x],
                      labels = c(gsub(
                        pattern = paste0(params$factors[x], "_"),
                        replacement = "",
                        x = unique(df_factors[[x]][["name"]])
                      ))) +
    scale_y_continuous(name = "Time to detection (years)") +
    labs(title = paste(w),
         subtitle = paste("Sensivitiy analysis: ", x))

    # bar plot - percentage of simulations where NIS not detected
  p2 <- ggplot(df_factors[[x]],
                aes(
                  x = name,
                  y = pct_no_detect / config$num_sim,
                  fill = name
                )) + # fill=name allow to automatically dedicate a color for each group
    geom_bar(stat = 'identity') +
    theme_bw() +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
    scale_x_discrete(name = params$factors[x],
                      labels = c(gsub(
                        pattern = paste0(params$factors[x], "_"),
                        replacement = "",
                        x = unique(df_factors[[x]][["name"]])
                      ))) +
    scale_y_continuous(name = "Simulations NIS not detected (%)",
                        limits = c(seq(
                          from = 0, to = 100, by = 10
                        )))

  # combine plots
  p1 + p2

  })
  
})

plots

```


#### Version

The version (sha) of https://github.com/CefasRepRes/NIS-intro-detect-sim repository used was: **`r system("git rev-parse HEAD", intern = TRUE)`**

```{r, echo = FALSE}
sessionInfo()
```

