---
title: "NIS-intro-detect-report-elasticity"
output: html_document
params:
  user_inputs: config
  factors: factors
  elasticity_dfs: elasticity_dfs
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("reshape2")
library("ggplot2")
```
\

**Date:** `r Sys.time()` \
**Author:** `r params$user_inputs$user` \
**Run Name:** `r params$user_inputs$run_name` \

\

The elasticity of each parameter within the NIS-intro-detect-sim script is tested and reported. Elasticity analysis is a method of comparing the sensitivity of each parameter where there is no scale in differences between parameters.

Three scenarios for site surveillance to detect non indigenous species (NIS) introduction are presented and the time to detection is reported.

* **A.** Random surveillance, where sites are visited at an equal rate independent of the risk of NIS introduction and establishment at each site.

* **B.** Risk-based surveillance, where sites with a higher probability of NIS introduction and establishment are visited at a higher visit rate due to their elevated risk.

* **C.** Heavy risk-based surveillance, where sites with higher probability of NIS introduction and establishment form the main focus of surveillance programmes and are visited at a substantially higher visit rate due to their elevated risk. 

\

#### Default Elasticity Parameters

The default parameters used for each run were as follows:

```{r, echo = F}
setNames(stack(config$defaults)[2:1], c("Parameter Name", "Input Value"))
```

The following input parameters (`r factors`) are increased and decreased by `r config$elasticity_proportion` to determine whether the parameter is elastic. An elasticity value > 1 indicates elasticity. An elasticity value between 0 and 1 is inelastic.

\

#### Elasticity Analysis

```{r, fig.height=10, fig.width = 6, fig.align='center', echo = F, warnings = FALSE}
# DATA WRANGLING -----------------------------------------
surveillance <- names(elasticity_dfs)

# for each of the surveillance strategy results
elasticity_dfs1 <- lapply(setNames(surveillance, surveillance), function(x) {
  
  lapply(names(elasticity_dfs[[x]]), function(y) {
    
    # place row names in column and reset row names
    new_df <- data.frame(names = row.names(elasticity_dfs[[x]][[y]]), elasticity_dfs[[x]][[y]], row.names = NULL)
    
  })
  
})

elasticity_dfs2 <- lapply(setNames(surveillance, surveillance), function(x) {
  # combine these data frames
  elasticity_df <- rbind(elasticity_dfs1[[x]][[1]], elasticity_dfs1[[x]][[2]])
  df_long <- reshape2::melt(elasticity_df, id.vars = c("names", "direction"))

  # convert columns to factor
  cols <- c("variable", "direction", "names")
  df_long[cols] <- lapply(df_long[cols], factor)
  
    # # make elastcity values positive
  df_long$value <- abs(df_long$value)

  return(df_long)
})


```


```{r, echo = FALSE, fig.width = 12, fig.height = 6, fig.align = 'center', warnings = FALSE}
# produce plots
lapply(surveillance, function(x) {
  
  ggplot(data = elasticity_dfs2[[x]],
       aes(x = names, y = value, color = direction)) + 
  geom_point() +
  facet_wrap(~ variable, ncol = 5, scales = "free_y") +
  theme_bw() +
  geom_hline(yintercept = 1, color = "dark gray") +
  ylab("Elasticity") +
  xlab("Parameter") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position = "bottom",
        legend.title = element_blank()) +
    ggtitle(x)
})

```

```{r, echo = FALSE, fig.width = 12, fig.height = 6, fig.align = 'center', warnings = FALSE}
elasticity_dfs3 <- data.table::rbindlist(elasticity_dfs2, idcol = "index")
elasticity_dfs3$index <- factor(elasticity_dfs3$index)

ggplot(data = elasticity_dfs3,
     aes(x = names, y = value, color = index, shape = direction)) + 
geom_point() +
facet_wrap(~ variable, ncol = 5, scales = "free_y") +
theme_bw() +
geom_hline(yintercept = 1, color = "dark gray") +
ylab("Elasticity") +
xlab("Parameter") +
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
      legend.position = "bottom",
      legend.title = element_blank())


```


#### Version

The version (sha) of https://github.com/CefasRepRes/NIS-intro-detect-sim repository used was: **`r system("git rev-parse HEAD", intern = TRUE)`**

```{r, echo = FALSE}
sessionInfo()
```

