---
title: "NIS-intro-detect-report"
output: html_document
params:
  user_inputs: !r config
  p_establish: p_establish
  p_intro: p_intro
  p_intro_establish: p_intro_establish
  resultsA: resultsA
  resultsB: resultsB
  resultsC: resultsC
  site_visit_rate_A: site_visit_rate_A
  site_visit_rate_B: site_visit_rate_B
  site_visit_rate_C: site_visit_rate_C
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("ggplot2")
library("patchwork")
```
\

**Date:** `r Sys.time()` \
**Author:** `r params$user_inputs$user` \
**Run Name:** `r params$user_inputs$run_name` \

\

Three scenarios for site surveillance to detect non indigenous species (NIS) introduction are presented and the time to detection is reported.

* **A.** Random surveillance, where sites are visited at an equal rate independent of the risk of NIS introduction and establishment at each site.

* **B.** Risk-based surveillance, where sites with a higher probability of NIS introduction and establishment are visited at a higher visit rate due to their elevated risk.

* **C.** Heavy risk-based surveillance, where sites with higher probability of NIS introduction and establishment form the main focus of surveillance programmes and are visited at a substantially higher visit rate due to their elevated risk. 

\

#### Input Parameters

```{r, echo = FALSE}
setNames(stack(params$user_inputs)[2:1], c("Parameter Name", "Input Value"))
```

\

#### Introduction and establishment probabilities across sites

For all three surveillance scenarios a probability of establishment, probability of introduction, and probability of introduction and establishment are randomly generated or calculated per site. These are displayed below.

\


```{r probabilities, echo = FALSE, fig.width = 12, fig.height = 4, fig.align = 'center'}
# generate data frame of probabilities
df_probs <- data.frame("p_establish" = params$p_establish,
                       "p_intro" = params$p_intro,
                       "p_intro_establish" = params$p_intro_establish)

# generate histograms of probabilities
p1 <- ggplot2::ggplot(df_probs, aes(x = p_establish)) +
  geom_histogram(binwidth = 0.05, colour = "black", fill = "gray") +
  theme_bw() +
  scale_x_continuous(name = "Probability of Establishment",
                     limits = c(0, 1)) +
  ylab("Frequency") +
  ggtitle("Probability of Establishment")

p2 <- ggplot2::ggplot(df_probs, aes(x = p_intro)) +
  geom_histogram(binwidth = 0.05, colour = "black", fill = "gray") +
  theme_bw() +
  scale_x_continuous(name = "Probability of Establishment",
                     limits = c(0, 1)) +
  ylab("Frequency") +
  ggtitle("Probability of Introduction")

p3 <- ggplot2::ggplot(df_probs, aes(x = p_intro)) +
  geom_histogram(binwidth = 0.05, colour = "black", fill = "gray") +
  theme_bw() +
  scale_x_continuous(name = "Probability of Establishment",
                     limits = c(0, 1)) +
  ylab("Frequency") +
  ggtitle("Probability of Introduction and Establishment")

# display plots side by side
p1 + p2 + p3

```

\

#### Site-specific visit rate for each surveillance scenario

Note that for each of these surveillance strategies the overall visit rate, as determined in the input parameters `mean_visit_rate` (in this run: `r params$user_inputs$mean_visit_rate`) remains the same. The site visit rate is artificially increased for sites with higher probability of introduction and establishment in risk-based surveillance and lowered for those with lower probability of introduction and establishment. These plots demonstrate this.

\

```{r, echo = FALSE, fig.width = 12, fig.height = 4, fig.align = 'center'}
# generate data frame of site visit rates
# added plus 0.05 to xlim as it was cutting off site visit rates all at 1.0
df_visits <- data.frame("site_visit_rate_A" = params$site_visit_rate_A,
                        "site_visit_rate_B" = params$site_visit_rate_B,
                        "site_visit_rate_C" = params$site_visit_rate_C)

p1 <- ggplot2::ggplot(df_visits, aes(x = site_visit_rate_A)) +
  geom_histogram(binwidth = 0.05, colour = "gray", fill = "gray") +
  theme_bw() +
  scale_x_continuous(name = "Site Visit Rate (per year)",
                     limits = c(0, max(df_visits$site_visit_rate_C)+0.05)) +
  
  ylab("Frequency") +
  
  ggtitle("Random Surveillance")

p2 <- ggplot2::ggplot(df_visits, aes(x = site_visit_rate_B)) +
  geom_histogram(binwidth = 0.05, colour = "lightblue2", fill = "lightblue2") +
  theme_bw() +
  scale_x_continuous(name = "Site Visit Rate (per year)",
                     limits = c(0, max(df_visits$site_visit_rate_C)+0.05)) +
  ylab("Frequency") +
  ggtitle("Risk-based surveillance")

p3 <- ggplot2::ggplot(df_visits, aes(x = site_visit_rate_C)) +
  geom_histogram(binwidth = 0.05, colour = "royalblue3", fill = "royalblue3") +
  theme_bw() +
  scale_x_continuous(name = "Site Visit Rate (per year)",
                     limits = c(0, max(df_visits$site_visit_rate_C)+0.05)) +
  ylab("Frequency") +
  ggtitle("Heavy risk-based surveillance")

p1 + p2 + p3

```

\

#### Time to detection for each site 

The time it takes in years to visit a site where the NIS has been introduced and also detect it is illustrated in the histograms below. Where an NIS introduction is not detected within the surveillance period of `r params$user_inputs$num_years` the time to detection reported is 100 year.

\


```{r, echo = FALSE, fig.width = 12, fig.height = 4, fig.align = 'center'}
# generate data frame of site visit rates
df_results <- data.frame("resultsA" = params$resultsA,
                         "resultsB" = params$resultsB,
                         "resultsC" = params$resultsC)

p1 <- ggplot2::ggplot(df_results, aes(x = resultsA)) +
  geom_histogram(binwidth = 0.05, colour = "gray", fill = "gray") +
  theme_bw() +
  ylab("Frequency") +
  ggtitle("Random surveillance") +
  scale_x_continuous(name = "Time to Detection (Years)",
                     limits = c(0, 101))

p2 <- ggplot2::ggplot(df_results, aes(x = resultsB)) +
  geom_histogram(binwidth = 0.05, colour = "lightblue2", fill = "lightblue2") +
  theme_bw() +
  ylab("Frequency") +
  ggtitle("Risk-based surveillance") +
  scale_x_continuous(name = "Time to Detection (Years)",
                     limits = c(0, 101))

p3 <- ggplot2::ggplot(df_results, aes(x = resultsC)) +
  geom_histogram(binwidth = 0.05, colour = "royalblue3", fill = "royalblue3") +
  theme_bw() +
  ylab("Frequency") +
  ggtitle("Heavy risk-based surveillance") +
  scale_x_continuous(name = "Time to Detection (Years)",
                     limits = c(0, 101))
p1 + p2 + p3

```

\

The time it takes in years to visit a site where the NIS has been introduced is also shown per simulation below.

\

```{r, echo = FALSE, fig.width = 12, fig.height = 4, fig.align = 'center'}

p1 <- ggplot2::ggplot(df_results, aes(x = 1:params$user_inputs$num_sim, y = resultsA)) +
  geom_point(color = "gray", shape = 1) +
  theme_bw() +
  xlab("Simulation") +
  scale_y_continuous(name = "Time to detection (Years)",
                     limits = c(0, 101)) +
  ggtitle("Random surveillance")
  
p2 <- ggplot2::ggplot(df_results, aes(x = 1:params$user_inputs$num_sim, y = resultsB)) +
  geom_point(color = "lightblue2", shape = 1) +
  theme_bw() +
  xlab("Simulation") +
  scale_y_continuous(name = "Time to detection (Years)",
                     limits = c(0, 101)) +
  ggtitle("Risk-based surveillance")

p3 <- ggplot2::ggplot(df_results, aes(x = 1:params$user_inputs$num_sim, y = resultsC)) +
  geom_point(color = "royalblue3", shape = 1) +
  theme_bw() +
  xlab("Simulation") +
  scale_y_continuous(name = "Time to detection (Years)",
                     limits = c(0, 101)) +
  ggtitle("Heavy risk-based surveillance")


p1 + p2 + p3

```

\

#### Probability of NIS Detection Over Time Depending on Surveillance Method

The probability of detection an NIS introduction over time using the three surveillance methods is also shown for quick visual comparison.

\

```{r, echo = FALSE, fig.width = 8, fig.height = 4, fig.align = 'center'}
df_scenarios <- data.frame("probability" = rep((0:(params$user_inputs$num_sim - 1)
                                                / params$user_inputs$num_sim - 1) + 1,
                                               times = 3),
                           "results" = c(sort(params$resultsA),
                                         sort(params$resultsB),
                                         sort(params$resultsC)),
                           "scenario" = rep(c("Random", "Risk-based", "Heavy risk-based"),
                                            each = params$user_inputs$num_sim))

df_scenarios$scenario <- factor(df_scenarios$scenario,
                                levels = c("Random",
                                           "Risk-based",
                                           "Heavy risk-based"))

ggplot2::ggplot(df_scenarios, aes(results, y = probability, group = scenario)) +
  geom_line(aes(color = scenario)) +
  theme_bw() +
  ggtitle("Probability of NIS Detection Through Time") +
  scale_x_continuous(name = "Time (Years)",
                     limits = c(0, params$user_inputs$num_years),
                     breaks = c(0:params$user_inputs$num_years)) +
  scale_y_continuous(name = "Probability of Detection\n",
                     limits = c(0, 1)) +
  guides(color = guide_legend("Surveillance Scenario")) +
  scale_color_manual(values = c("gray", "lightblue2", "royalblue3"))

```

\

#### Summary of detection times:

**A:** Random surveillance

```{r, echo = FALSE}
summary(params$resultsA[!params$resultsA == 1000])
```

\

**B:** Risk-based surveillance

```{r, echo = FALSE}
summary(params$resultsB[!params$resultsB == 1000])
```

\

**C:** Heavy risk-based surveillance

```{r, echo = FALSE}
summary(params$resultsC[!params$resultsC == 1000])
```

\

#### Simulations with No Detections (%):

**A:** Random surveillance

```{r, echo = F}

(length(params$resultsA[params$resultsA == 1000])/length(params$resultsA))*100

```

**B:** Risk-based surveillance

```{r, echo = F}

(length(params$resultsB[params$resultsB == 1000])/length(params$resultsB))*100

```

**C:** Heavy risk-based surveillance

```{r, echo = F}

(length(params$resultsC[params$resultsC == 1000])/length(params$resultsC))*100

```

#### Version

The version (sha) of https://github.com/CefasRepRes/NIS-intro-detect-sim repository used was: **`r system("git rev-parse HEAD", intern = TRUE)`**

```{r, echo = FALSE}
sessionInfo()
```

